DATA 621 Homework #4

### 2019-11-04 hw4/HW4.Rmd
Updated HW4

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(dplyr)
library(Amelia)
library(kableExtra)
library(caret)
library(DMwR)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

There are missing values for the `CAR_AGE` and `YOJ`(Years on Job) variables.  We will fill in the missing variables using KNN.

```{r}
set.seed(42)
knn <- knnImputation(df)
impute_me <- is.na(df$CAR_AGE)
df[impute_me,"CAR_AGE"] <- knn[impute_me,"CAR_AGE"] 
impute_me <- is.na(df$YOJ)
df[impute_me,"YOJ"] <- knn[impute_me,"YOJ"] 
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(gridExtra)
library(dplyr)
library(Amelia)
library(kableExtra)
library(caret)
library(DMwR)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

There are missing values for the `CAR_AGE`, `YOJ`(Years on Job), and `AGE` variables.  We will fill in the missing variables using KNN.

```{r}
set.seed(42)
knn <- knnImputation(df)
impute_me <- is.na(df$CAR_AGE)
df[impute_me,"CAR_AGE"] <- knn[impute_me,"CAR_AGE"] 
impute_me <- is.na(df$YOJ)
df[impute_me,"YOJ"] <- knn[impute_me,"YOJ"]
impute_me <- is.na(df$AGE)
df[impute_me,"AGE"] <- knn[impute_me,"AGE"]
```
